Foreign Exchange Speculation: An Event Study

### 2018-01-15 MDPI/MDPI_template/FinStudies.tex
The pdf can be created.

\begin{document}
\section{Introduction}
If speculation is based on information it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium. \citet{KeynesHedge} and \citet{HicksHedge} for example emphasise the role that speculation plays in facilitating financial market transactions. Speculators offer a service for a fee that is determined by the return on their activity.  While speculators may be trading on information or noise, informed speculators will tend to drive out the uninformed noise-traders according to \citet{FriedmanPositive}.   However, the later \citet[p. 101]{Keynes1936} regarded speculation as a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd' and \citet{Delong1990noise} provides a model of cases where speculative noise provides a constrain on informed traders benefiting from their knowledge. Now speculation is an uninformed and destabilising force.  \added[remark=1]{We have therefore two concepts of speculation: one that is random and disruptive and one that is informed and beneicial in its provison of liqidity.

@@

\section{Measuring speculation}
\replaced{This study uses a unique series of option}{A set of} \emph{risk-reversal skews}\added{are used} to measure \delete{of} speculative sentiment\footnote{\deleted{It appears that this is the only period for which the data currently exist.  The risk-reversal data is very difficult to obtain in an over-the-counter market like foreign exchange where there is no centralised exchange to record and collect information, generally being the property of quoting institutions.}  The risk-reversals are the average prices quoted at 10:00 GMT by major banks on the Thomson-Reuters composite option pages (OPT1)  for the period between January 2 1996 and September 6 2002.  The risk-reversals are the spread of implied volatility for a 1 month 25 delta at-the-money call option relative to the equivalent put.  Risk-reversal skew is the relative price of currency put and call options for the same strike price.}\delete{, as well as CFTC data on speculative positions.} The risk-reversal skew is the relationship between a call option and the equivalent put.    If the exchange rate is expected to follow a random walk with drift towards the 1 month forward \added[remark=4]{the same maturity as the option}, implied volatility on the put and the call for the same delta should be equal.  Any deviation from this equivalence is an indication that a divergence from the random walk with drift is implied in the market price of options.

\added{It is common practice to back market expectations out of information drawn from option prices.  \footnote{If the risk-reversal for a 1-month USD/CAD is quoted at 0.15-0.28\% and the implied volatility is 8.50\%, the market-maker would be willing to buy the 1-month 25 delta USD-put-CAD-call at 8.65\% and sell the USD-call-CAD-put at 8.50\%.  The dealer pays 0.15\%.  Alternatively, the dealer would sell a 25 delta call at 8.78\% and buy the USD-call-CAD-put at 8.50\%, earning 0.28\%. See \citet{Global} for a technical review. }  Therefore, the relationship between implied volatility for calls and implied volatilities for puts for the same delta and maturity strike is an indication of how much more expensive calls are relative to the equivalent put or as the market bias towards puts over calls and as an indication of market sentiment or related market positioning.  The larger the absolute level of the risk-reversal skew, the greater the relative price and, if the deviation is based on information, subsequent price action should be zero on average; if the deviation is based on noise, this movement should be reversed.  See \citet{Yan2011} and \citet{FengZhangFriesen} for some analysis of implied volatility in the equity market.

@@

\begin{figure}
\graphicspath{{../Figures/}}
\centering
\includegraphics[scale=0.8]{FPCum6w}
\caption{Event Study:  Extreme ($90^{th}$ percentile), Non-commercial net long (S1), 6 week window. Non-commercial net per OI (S2) are the net speculative positions (as reported to US regulator the CFTC) relative to all open positions; extreme high is at or above the $90^{th}$ percentile for the whole range, cumulative returns are the sum of log exchange rate returns. The event day is the day of the extreme reading as a measure of extreme speculative activity.  If speculation is uninformed, extremes should be followed by reversals; if speculation is informed, extremes are more likely to be followed by a random walk.}

\begin{figure}
\graphicspath{{../Figures/}}
\centering
\includegraphics[scale=0.8]{FPCum6wa}
\caption{Event Study:  Extreme ($90^{th}$ percentile), Non-commercial net long (S1), 6 week window. Non-commercial net per OI (S2) are the net speculative positions (as reported to US regulator the CFTC) relative to all open positions; extreme high is at or above the $90^{th}$ percentile for the whole range, cumulative returns are the sum of log exchange rate returns. The event day is the day of the extreme reading as a measure of extreme speculative activity.  If speculation is uninformed, extremes should be followed by reversals; if speculation is informed, extremes are more likely to be followed by a random walk.}

\label{fig:ES4}
\end{figure}

>>>>

\begin{document}
\section{Introduction}
If speculation is based on information it is a stabilising force, providing liquidity and helping to ensure that markets swiftly find equilibrium. \citet{KeynesHedge} and \citet{HicksHedge} for example emphasise the role that speculation plays in facilitating financial market transactions. Speculators offer a service for a fee that is determined by the return on their activity.  While speculators may be trading on information or noise, informed speculators will tend to drive out the uninformed noise-traders according to \citet{FriedmanPositive}.   However, the later \citet[p. 101]{Keynes1936} regarded speculation as a myopic, sentiment-driven activity, dominated by the desire to ``beat the gun'' or  ``outwit the crowd' and \citet{Delong1990noise} provides a model of cases where speculative noise provides a constrain on informed traders benefiting from their knowledge. Now speculation is an uninformed and destabilising force.  \added{We have therefore two concepts of speculation: one that is random and disruptive and one that is informed and beneicial in its provison of liqidity.

@@

\section{Measuring speculation}
\replaced{This study uses a unique series of option}{A set of} \emph{risk-reversal skews}\added{are used} to measure \deleted{of} speculative sentiment\footnote{\deleted{It appears that this is the only period for which the data currently exist.  The risk-reversal data is very difficult to obtain in an over-the-counter market like foreign exchange where there is no centralised exchange to record and collect information, generally being the property of quoting institutions.}  The risk-reversals are the average prices quoted at 10:00 GMT by major banks on the Thomson-Reuters composite option pages (OPT1)  for the period between January 2 1996 and September 6 2002.  The risk-reversals are the spread of implied volatility for a 1 month 25 delta at-the-money call option relative to the equivalent put.  Risk-reversal skew is the relative price of currency put and call options for the same strike price.}\deleted{, as well as CFTC data on speculative positions.} The risk-reversal skew is the relationship between a call option and the equivalent put.    If the exchange rate is expected to follow a random walk with drift towards the 1 month forward \added[remark=4]{the same maturity as the option}, implied volatility on the put and the call for the same delta should be equal.  Any deviation from this equivalence is an indication that a divergence from the random walk with drift is implied in the market price of options.

\added{It is common practice to back market expectations out of information drawn from option prices.}  \footnote{If the risk-reversal for a 1-month USD/CAD is quoted at 0.15-0.28\% and the implied volatility is 8.50\%, the market-maker would be willing to buy the 1-month 25 delta USD-put-CAD-call at 8.65\% and sell the USD-call-CAD-put at 8.50\%.  The dealer pays 0.15\%.  Alternatively, the dealer would sell a 25 delta call at 8.78\% and buy the USD-call-CAD-put at 8.50\%, earning 0.28\%. See \citet{Global} for a technical review. }  Therefore, the relationship between implied volatility for calls and implied volatilities for puts for the same delta and maturity strike is an indication of how much more expensive calls are relative to the equivalent put or as the market bias towards puts over calls and as an indication of market sentiment or related market positioning.  The larger the absolute level of the risk-reversal skew, the greater the relative price and, if the deviation is based on information, subsequent price action should be zero on average; if the deviation is based on noise, this movement should be reversed.  See \citet{Yan2011} and \citet{FengZhangFriesen} for some analysis of implied volatility in the equity market.

@@

\begin{figure}
\graphicspath{{../Figures/}}
\centering
\includegraphics[scale=0.8]{FPCum6w}
\caption{Event Study:  Extreme ($90^{th}$ percentile), Non-commercial net long (S1), 6 week window. Non-commercial net per OI (S2) are the net speculative positions (as reported to US regulator the CFTC) relative to all open positions; extreme high is at or above the $90^{th}$ percentile for the whole range, cumulative returns are the sum of log exchange rate returns. The event day is the day of the extreme reading as a measure of extreme speculative activity.  If speculation is uninformed, extremes should be followed by reversals; if speculation is informed, extremes are more likely to be followed by a random walk.}
\label{fig:ES3}
\end{figure}

\begin{figure}
\graphicspath{{../Figures/}}
\centering
\includegraphics[scale=0.8]{FPCum6wa}
\caption{Event Study:  Extreme ($90^{th}$ percentile), Non-commercial net long (S1), 6 week window. Non-commercial net per OI (S2) are the net speculative positions (as reported to US regulator the CFTC) relative to all open positions; extreme high is at or above the $90^{th}$ percentile for the whole range, cumulative returns are the sum of log exchange rate returns. The event day is the day of the extreme reading as a measure of extreme speculative activity.  If speculation is uninformed, extremes should be followed by reversals; if speculation is informed, extremes are more likely to be followed by a random walk.}
\label{fig:ES4}
\end{figure}
